Data Formatting

### 2021-05-19 scripts/data_format.Rmd
redo with pairwise distances

Phylogeny
```{r}
resolved <- tnrs_match_names(names$tnrs_name)
resolved$unique_name <- gsub(" ", "_",resolved$unique_name)
resolved$search_string <- paste(toupper(substr(resolved$search_string, 1, 1)), 
                                  substr(resolved$search_string,2,nchar(resolved$search_string)),sep = "")

resolved %<>% rename("species_name" = "search_string") %>% select(species_name, unique_name, ott_id)

>>>>

Phylogeny
```{r}
resolved <- tnrs_match_names(names$tnrs_name)
resolved %<>% rename("tnrs_name" = "unique_name")
#resolved$search_string <- paste(toupper(substr(resolved$search_string, 1, 1)), 
#                                  substr(resolved$search_string,2,nchar(resolved$search_string)),sep = "")

resolved %<>% select(tnrs_name, ott_id)
